Ensemble Stability of Biological Networks

### 2014-09-18 paper.tex
minor edits
edit abstract and intro

Here we build on work aimed at investigating the stability of randomly connected dynamical systems to state-based perturbations. We precisely compute the probability of stability as a distribution over system connectivity for all systems containing two interacting components. We then proceed to determine the probability of structural stability over the same domain. We find that while stability to perturbations in the state of this class of dynamical systems is independent of system connectivity, perturbations to the magnitude of connections is correlated with connectivity in a non-linear manner. This work reestablishes and clarifies a thread of research that is extremely important for the continuing development of systems biology.

@@

\section{Tables}
\input{tex/table2x2stab}
\input{tex/tablenographs}
% \input{tex/tablewithgraphs}

>>>>

Here we build on work aimed at investigating the stability of randomly connected dynamical systems to structural perturbations. We precisely compute the probability of stability as a distribution over system connectivity for all systems containing two or three interacting components. We then proceed to determine the probability of \emph{structural stability} or \emph{robustness} which is the distribution of stability to perturbation in the system structure for systems which are determined to be stable \cite{Smale1967}. This quantity is of interest at all scales of the biological hierarchy, and has been previously addressed in the study of the robustness of gene-regulatory networks \cite{WADDINGTON1942a,VanNimwegen1999,Siegal2002,Ciliberti2007b,Ciliberti2007,Wagner2013}. We find that stability to structural perturbations of this class of dynamical systems is correlated with connectivity, number of cycles, and the number of links between strongly connected components of the underlying interdependency graph. The latter derives from the fact that the permutation of strongly connected components is a symmetry of system robustness. This work clarifies a thread of research that is extremely important for the continuing development of systems biology.

@@

\section{Tables}
\input{tex/table2x2stab}
\input{tex/tablenographs}

% \newpage

% \input{tex/tablewithgraphs}
